The effect of genetic linkage on island endemics richness

### 2018-08-03 paper/draft.tex
add some refs

We use an individual-based spatially and temporally explicit metacommunity model written in julia %\cite{JULIALANG}.
The model considers competition between individuals, environmental niche adaptation, density independent mortality,
dispersal, sexual reproduction and mutation.
Individuals are characterized by a lineage identifier,
body mass, age and fitness.
Each individual's life history traits (table) are coded by mutable genes \cref{fig:schematic}.
The genes, in turn, may be combined to linkage units (``chromosomes'').
Genes in a linkage unit are considered a heredetary unit.
This means that they will always be inherited in junction.
Thus, only complete linkage units will be subject to recombination.

@@

A detailed protocol can be found in the appendix (\cite{grimm2010odd}, XXX).

>>>>

We use an individual-based spatially and temporally explicit metacommunity model written in julia \cite{bezansonJuliaFreshApproach2017}.
The model considers competition between individuals, environmental niche adaptation, density independent mortality,
dispersal, sexual reproduction and mutation.
Individuals are characterized by a lineage identifier,
body mass, age and fitness.
Each individual's life history traits (table) are coded by mutable genes \cref{fig:schematic}.
The genes, in turn, may be combined to linkage units (``chromosomes'').
Genes in a linkage unit are considered a heredetary unit.
This means that they will always be inherited in junction.
Thus, only complete linkage units will be subject to recombination.

@@

A detailed protocol can be found in the appendix \cite{grimmStandardProtocolDescribing2006a} \cite{grimmODDProtocolReview2010}.
